Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

@@

\subsection{Node labeling}
NSPDK takes labeled graphs as its input to proceed. Therefore, graph node labeling is a step needs to be done before employing NSPDK for graph similarity measure. Here, we propose a node labeling function $\ell$ which assigns labels for nodes based on node degrees. First, we use the degree values for their labels for nodes having degree less than or equal 5. We then discretize the degrees larger than a user defined threshold $T$ ($T=5$ in our experimental evaluation) into $k$ bins and assign the same label for nodes belong to the same bin. We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties. Formally, the function is defined as:
\begin{center}
$\ell(u) = \left\{
	\begin{array}{ll}
		d(u),\  & \mbox{if } d(u) \leq T \\
		T+i,\ & \mbox{if } d(u) > T
	\end{array}
\right.$,
\end{center}
where $i = \lceil \frac{d(u)-T}{bin}\rceil$, $bin = \frac{d(G)-T}{\lambda - T}$ and $\lambda$ ($\lambda > T$) is the number of labels used to label for nodes in the graphs. The value of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.
\subsection{Link representation}
Most methods for link prediction attempt to computes similarities between nodes and consider to rank links. We desire to take links as examples to learn and predict. Therefore, we propose a method which model the context of two nodes to represent for link connecting them.

Let us consider two nodes $u$ and $v$ ($u, v \in V$), we first extract two neighborhood subgraphs with radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively. We then create an artificial node $w$. This node is connected to both $u$ and $v$. As a consequence, we achieve a single graph representing for a link connecting $u$ and $v$.
\subsection{Joint neighborhood subgraphs link prediction}
Given a graph $G(V,E)$ and a set of links $L = \lbrace(u,v)\ |\ (u,v)\in\ O\ or\ (u,v)\in U \rbrace$, our method consists five steps:
\begin{itemize}
	\item Node labeling: Nodes in $G$ are labeled using a defined node label function $\ell$.
	\item Link representing: Link in $L$ are represented as joint neighborhood subgraphs. As a result, we have a set of graphs $SG = \lbrace G_{uv}\ |\ (u,v) \in L \rbrace$
	\item Kernel computation: Obtained graph set $SG$ is used to compute a gram matrix, $K$, by using NSPDK. $K$ shows the similarities between graphs (links).
	\item Model configuration: $K$ is then fed into a kernel machine to build a model which tries to learn a function to separate observed links from non-observed ones in the sense of properties.
	\item Scoring and ranking: Now the model is used to return scores for coming links. These scores are used to rank links from the most to the least probable of being present in the graph.
\end{itemize}

>>>>

\subsection{Link encoding as subgraphs union}
Most methods for link prediction compute pairwise nodes similarities treating  the nodes defining the candidate edge independently. Instead we propose to jointly consider both candidate endpoint nodes together with their extended ''context''. To do so we build a graph starting from the two nodes and the underlying network. Given nodes $u$ and $v$, we first extract the two neighborhood sets with a user defined radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively. We then consider the graph $\mathcal{J}$ induced by the set union $N_R(u) \cup N_R(u)$. Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{key}).

\subsection{Node labeling}
We propose to use a graph kernel approach to classify the subgraphs encoding each link. In our setup nodes are not endowed with any ''side'' information. However to increase the discriminative power of the similarity notion induced by the graph kernel, instead of assuming a dummy, non-informative label on each node, we propose to use a node labeling function $\ell$ which assigns a discrete label as the node degree. As the degree distribution can in principle extend to large values, we employ a  discretization technique. 
First, we use the degree values for their labels for nodes having degree less than or equal 5. We then discretize the degrees larger than a user defined threshold $T$ ($T=5$ in our experimental evaluation) into $k$ bins and assign the same label for nodes belong to the same bin. We label for nodes owning similar degrees with the same label due to the assumption that nodes with similar degrees tend to share common properties. Formally, the function is defined as:
\begin{center}
$\ell(u) = \left\{
	\begin{array}{ll}
		d(u),\  & \mbox{if } d(u) \leq T \\
		T+i,\ & \mbox{if } d(u) > T
	\end{array}
\right.$,
\end{center}
where $i = \lceil \frac{d(u)-T}{bin}\rceil$, $bin = \frac{d(G)-T}{\lambda - T}$ and $\lambda$ ($\lambda > T$) is the number of labels used to label for nodes in the graphs. The value of $\lambda$ depend on the histogram of graph node degree. We can use tuning technique in order to obtain suitable value for $\lambda$.

@@

\subsection{Joint neighborhood subgraphs link prediction}
Given a graph $G(V,E)$ and a set of links $L = \lbrace(u,v)\ |\ (u,v)\in\ O\ or\ (u,v)\in U \rbrace$, our method consists five steps:
\begin{itemize}
	\item Node labeling: Nodes in $G$ are labeled using a defined node label function $\ell$.
	\item Link representing: Link in $L$ are represented as joint neighborhood subgraphs. As a result, we have a set of graphs $SG = \lbrace G_{uv}\ |\ (u,v) \in L \rbrace$
	\item Kernel computation: Obtained graph set $SG$ is used to compute a gram matrix, $K$, by using NSPDK. $K$ shows the similarities between graphs (links).
	\item Model configuration: $K$ is then fed into a kernel machine to build a model which tries to learn a function to separate observed links from non-observed ones in the sense of properties.
	\item Scoring and ranking: Now the model is used to return scores for coming links. These scores are used to rank links from the most to the least probable of being present in the graph.
\end{itemize}
